Effects of CHILDREN's programs

### 2020-02-26 paper.tex
recoded factor scales from numbers to strings

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 19:01:58 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{fundamentalDynamics}
\end{table}

@@

{\centering \includegraphics[width=0.8\textwidth]{figure/Grant_Trend-1}

@@

In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the degree to which beneficiaries: are healthier, have a growing appreciation for a healthier diet, and have increased their knowledge about what constitutes a healthy diet. Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For this figure, we use the original ordinal varibles which result from the survey structure.

@@

{\centering \includegraphics[width=0.8\textwidth]{figure/Health_time_plots-1}

@@

\end{knitrout}
\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

@@

In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities. These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise. Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.

@@

{\centering \includegraphics[width=0.8\textwidth]{figure/Equality_time_plots-1}

@@

As table \ref{GrantsRegressionsLunch} shows, this is emphatically true. Whether we look at the original data set, the one without outliers and the one with imputed values, a strong association becomes evident. 
The estimated coefficents are very similar when we use the original dataset and the one with imputed values. In the case of the original data set, increasing the subsidy to an organization by one EUR is associated with 2.6 additional meals dispensed. This estimate is highly statistically significant. When we exclude outliers, i.e. those organizations that give out very many menus or very few menus,
the estimated coefficent decreases by about one order of magnitude. Still, spending not much more than three EUR more goes hand in hand with one extra meal. The estimate is also highly statistically significant.

@@

In the remit of the Trips program, the picture looks much different.

@@

@@

In the next section, we want to explore the influence of the DGE Criterion on relevant health outcomes.

@@

\end{knitrout}
\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are. It is based on the criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung). According to information from CHILDREN, they ask the organizations to send them their menus. An ecotrophologist collaborating with CHILDREN assesed the menus. In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

@@

\subsection{Variables of interest: selfworth and everyday expertise as proxies for equality of opportunities}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 19:02:05
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 19:02:06
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Less Ill} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 19:02:06
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Dietary Knowledge} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 19:02:06
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Appreciate Healthy} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 19:02:06
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Equality of opportunities, selfworth} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 19:02:06
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Equality of opportunities, everyday expertise} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -3.543 & 0.343 & -10.330 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -0.736 & 0.132 & -5.563 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.764 & 0.157 & 11.249 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00003 & 0.00001 & -4.070 & 0.00005 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}\end{kframe}

>>>>

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 22:15:10 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{fundamentalDynamics}
\end{table}

@@

{\centering \includegraphics[width=0.8\textwidth]{figure/GrantTrend-1}

@@

In its yearly surveys, CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet. Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For this figure, we use the original ordinal varibles which result from the survey structure.

@@

{\centering \includegraphics[width=0.8\textwidth]{figure/HealthTimePlots-1}

@@

\end{knitrout}
\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

@@

In its yearly surveys, CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities. These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise. Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.

@@

{\centering \includegraphics[width=0.8\textwidth]{figure/EqualityTimePlots-1}

@@

As table \ref{GrantsRegressionsLunch} shows, this is emphatically true. Whether we look at the original data set, the one without outliers and the one with imputed values, a strong association becomes evident. 
The estimated coefficients are very similar when we use the original dataset and the one with imputed values. In the case of the original data set, increasing the subsidy to an organization by one EUR is associated with 2.6 additional meals dispensed. This estimate is highly statistically significant. When we exclude outliers, i.e. those organizations that give out very many menus or very few menus,
the estimated coefficient decreases by about one order of magnitude. Still, spending not much more than three EUR more goes hand in hand with one extra meal. The estimate is also highly statistically significant.

@@

In the remit of the Trips program, the picture looks much different. In the case of the original data set and the data set with imputed variables, an increase in the trips subsidy by 5000 EUR is needed for an extra trip. The coefficent of 0.0002 is statistically significant at the 5\% level. As soon as outliers are excluded, the coefficent changes to 0.0003, which is highly statistically significant. This means that, according to this model, at least 3000 EUR are needed for an additional trip.
In sum, there seems to be no clear connection between how much money CHILDREN gives to an organization and the number of trips it organizes.

@@

\subsection{Variables of interest: selfworth and everyday expertise}

In their surveys, CHILDREN asks about two variables in both programs. These are the share of beneficiaries that are believed to have increased their self-worth and to have ehanced their everyday expertise. This feature could potentially allow us to compare the two programs regarding their realtive effectiveness. Like always, we standardize the two outcome variables. As before, we can only make associational claims. We invariably find no clear-cut relationship between the subsidy per beneficiary and the two outcomes. In fact, no coefficent is statistically significantly differnent from zero at any of the usual levels.

Tables \ref{SelfworthRegressions} and \ref{DayToDaySkillsRegressions} present the null results.

@@

Now, we turn to a predictor that CHILDREN does not directly influence until now, but that it easily could. In 2014, 2016, 2017 and 2018 the organizations had to send CHILDREN a sample of their menus. An ecotrophologist collaborating with CHILDREN assessed those menus with regards to how healthy they were. This assessment was based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).

In its yearly surveys, CHILDREN asks about three variables closely related to a healthy diet. These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.

Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion and each of the three health-related variables. The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.

We use standardized versions of these variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
If we estimated these models with ordinary least squares, we would ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so. To control for this difference in size, we fit the models with weighted least squares, using the number of beneficiaries as weights.

@@

\end{knitrout}
\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are. It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung). According to information from CHILDREN, they ask the organizations to send them a sample of their menus. An ecotrophologist collaborating with CHILDREN assessed the menus. In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

@@

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Less Ill} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Dietary Knowledge} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Appreciate Healthy} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Equality of opportunities, selfworth} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Equality of opportunities, everyday expertise} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -3.543 & 0.343 & -10.330 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -0.736 & 0.132 & -5.563 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.764 & 0.157 & 11.249 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00003 & 0.00001 & -4.070 & 0.00005 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

% <<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
% #expanded model less ill 
% 
% lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
% lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
% elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.Rds")
% @
